Self-test prime dimensional EPR pairs with constant alphabet

### 2019-02-05 Draft/draft.tex
I read up to the middle of page 10, and added more comments

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\end{proof}
Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
odd prime number $d$.

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
	\end{align}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}
	Expanding $\tilde{Z}_B^2$ we get
	\begin{align*}
		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
	\end{align*}
	so we can derive that 
	\begin{align}
	\label{eq:eig_v}
		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
	\end{align}
	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.
	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
	\begin{align}
		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
	\end{align}
	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
	\begin{align*}
		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
	\end{align*}
	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.

@@

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
We remark that for the extended weighted CHSH test, the primitive root of $d$ is irrelevant,
so we drop the superscript $(r)$.

In this test, Alice and Bob each gets a question $x$,$y \in \{ 1, 2, \ast\}$ and 
they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
The correlation $C(\dr{2})$ is the optimal correlation of this test.
Before presenting the optimal correlation, we give intuitions about how the players should behave.
\begin{itemize}
	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	their answer should agree;
	\item \textbf{Case 2a:} when $x,y \in \{1,2\}$ and if they answer with $a,b \in \{0,1\}$, then
	their answers are scored according to $I_{\cot(-\pi/d)}$;
	\item \textbf{Case 2b:} when $x,y \in \{1,2\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
	\item \textbf{Case 3:} when $x \in {1,2}, y = \ast$, if Bob answers $\diamond$, 
	Alice should answer with $\{0.1\}$ but not $\perp$,
	if Bob answers $\perp$, Alice should answer $\perp$ too.
\end{itemize}
\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and
define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
maximize $\langle I_{\cot(-\pi/d)} \rangle$.

@@

>>>>

To summarize, we have proven that $x_{k,l} = 0$ for all $k$ and $l$, which implies that the elements of the set
$\{ U^k X^l \}$ are linearly independent and forms a basis for the ring of all the $(d-1)\times(d-1)$ matrices over $\C$.
\carl{Nice proof.  I like the use of the Vandermonde matrix.  We can think a little about possible simplifications.}
\end{proof}
Note that the primitive root $r$ in the lemma is not restricted to the set $\{2,3,5\}$, so this lemma works for any 
odd prime number $d$.

@@

%======================================
\section{The extended weighted CHSH test}
\label{sec:chsh}
%======================================
Before introducing the extended weighted CHSH test, we fill in some background about the weighted CHSH inequality,
namely, that its maximal violation can self-test $2$-dimensional EPR pair and rotated Pauli operators.
The robust self-testing result is summarized in the following theorem.
\begin{theorem}
\label{thm:selftest}
	Suppose the quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the violation
	at least $2\sqrt{1+\alpha^2} - \epsilon$
	for some $\epsilon$, then
	there exists a local isometry $\Phi = \Phi_A \x \Phi_B$ and an auxiliary state $\ket{aux}$  such that
	\begin{align}
		\| \Phi( \tilde{A}_x \x \tilde{B}_y \ket{\psi}) -\ket{junk} \x (A_x \x B_y) \ket{\EPR{2}}  \| = O((\alpha+\frac{1}{\alpha}) \sqrt{\epsilon})
	\end{align}
	for $x,y \in \{0, 1, 2\}$ where the subscript $0$ refers to the identity operator and $A_x, B_y$ are 
	defined in \cref{def:ideal}.  \carl{You're using both ``aux'' and ``junk'' for the auxilliary state.  Also you need
	to be clearer about what label you are using for Alice's and Bob's systems (see my previous comment on this).}
\end{theorem}
Our approach is very similar to the one used in Ref.~\cite{bamps2015} so we 
defer the proof of \cref{thm:selftest} till \cref{sec:selftest}.
After proving the robust self-testing result, we take one step further and observe an interesting property of the 
product of Bob's observables.
\begin{proposition}
\label{prop:2d-subspace}
	Let $\mu = \arctan(1/\alpha)$ for some $\alpha$.
	Suppose a quantum strategy $(\ket{\tpsi}, \{\tilde{A}_x\}_{x \in [2]+1}, \{\tilde{B}_y\}_{y \in [2]+1})$ achieves the maximal 
	violation of  $\I_{\alpha}$, then $\tilde{B}_0\tilde{B}_1$ has eigenvalues $e^{i2\mu}$ and $e^{-i2\mu}$.  \carl{Make clear
	that we mean that these are the only eigenvalues.}
\end{proposition}
\begin{proof}[Proof of \cref{prop:2d-subspace}]
	Following the argument in the proof of \cref{thm:selftest} in \cref{sec:selftest}, we know
	$\tilde{Z}_B = (\tB_1+\tB_2)/2\cos(\mu)$ is a binary observable. \textcolor{red}{HF: Do we need to justify it?}  \carl{Yes,
	you should say more specifically where that is proved.}
	Expanding $\tilde{Z}_B^2$ we get
	\begin{align*}
		\1 = \tilde{Z}_B^2 = \frac{\tB_1^2 + \tB_1\tB_2 + \tB_2\tB_1 + \tB_2^2}{4\cos(\mu)^2}
		=\frac{2\1 + \tB_1\tB_2 + \tB_2\tB_1}{4\cos^2(\mu)},
	\end{align*}
	so we can derive that 
	\begin{align}
	\label{eq:eig_v}
		\tB_1\tB_2 + \tB_2\tB_1 = 2(2\cos^2(\mu)-1)\1 = 2 \cos(2\mu) \1.
	\end{align}
	Observe that $(\tB_1\tB_2)^\dagger = \tB_2\tB_1$ and 
	$(\tB_2\tB_1)(\tB_1\tB_2) = \tB_2\1\tB_2 = \1$, then we can conclude that $\tB_1\tB_2$ is unitary.  \carl{(It's a product
	of unitaries, so that step is immediate.)}
	Suppose the eigen-decomposition of $\tB_1\tB_2$ is
	\begin{align}
		\tB_1\tB_2 = \sum_{i=1}^m \lambda_i \ketbra{i}{i}
	\end{align}
	for some orthonormal set of eigenvectors $\{ \ket{i} \}_{i=1}^m$
	and $\norm{\lambda_i} =1$ for $1 \leq i \leq m$.
	Eq.~\ref{eq:eig_v} tells us that for each $1 \leq i \leq m$
	\begin{align*}
		\lambda_i + \lambda_i^{-1} = 2\Re(\lambda_i) = 2 \cos(2\mu),
	\end{align*}
	so we can conclude that $\lambda_i = e^{i 2\mu}$ or $e^{-i 2\mu}$.  \carl{Good proof (if you fill in the step at
	the beginning).}

@@

The extended weighted CHSH test is added to make sure that the operator $X$ extracted from 
Alice and Bob's operator solution of $\LS$ has eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
In \cref{sec:main}, we will reason why showing these two eigenvalues is enough to guarantee that 
$X$ has the eigen-structure required by \cref{lm:ux_independ}.
We denote this game that enforces the eigenvalues of the observable $X$ by
$\CHSH_X$, where the superscript $d$ emphasizes that the scoring rules of this game depend on $d$.
We remark that for the extended weighted CHSH test, the primitive root of $d$ is irrelevant,
so we drop the superscript $(r)$.
\carl{You need to be more clear --- after reading this, I am still not sure what mathematical object ``$\CHSH_X$'' refers to.}

In this test, Alice and Bob each gets a question $x$,$y \in \{ 1, 2, \ast\}$ and 
they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
The correlation $C(\dr{2})$ is the optimal correlation of this test.
Before presenting the optimal correlation, we give intuitions about how the players should behave.
\begin{itemize}
	\item \textbf{Case 1:} when $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	their answer should agree;
	\item \textbf{Case 2a:} when $x,y \in \{1,2\}$ and if they answer with $a,b \in \{0,1\}$, then
	their answers are scored according to $I_{\cot(-\pi/d)}$;
	\item \textbf{Case 2b:} when $x,y \in \{1,2\}$ and if Alice answers with $\perp$, then all Bob's answers are irrelevant;
	\item \textbf{Case 3:} when $x \in {1,2}, y = \ast$, if Bob answers $\diamond$, 
	Alice should answer with $\{0.1\}$ but not $\perp$,
	if Bob answers $\perp$, Alice should answer $\perp$ too.
\end{itemize}
\textbf{The ideal strategy and ideal correlation}. Alice and Bob share the state $\ket{\psi} =\frac{1}{\sqrt{d-1}} \sum_{i=1}^{d-1} \ket{u_i}\ket{u_i}$.
We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ \carl{(That's not 
the way I usually see the $\setminus$ symbol used.)} and
define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
maximize $\langle I_{\cot(-\pi/d)} \rangle$.

@@

\carl{This good, but I imagine a reader being a little confused about what you are doing
with these correlations (since the previous subsection wasn't very clear).}
